Software Citation Principles

### 2016-07-20 sc-principles/software-citation-principles.tex
softened recommendation on paper citation

Currently, and for the foreseeable future, software papers are being published and cited,
in addition to software itself being published and cited, as many community norms and practices are
oriented towards citation of papers.
As discussed in the Importance principle~(\ref{principle:importance}) and the discussion above, \textit{the software
itself should be cited on the same basis as any other research product; authors should cite the appropriate set of software products}.
If a software paper exists and it contains results (performance, validation, etc.) that are
important to the work, then the software paper should also be cited.
In addition, if the software authors ask that a paper should be cited, that should typically be respected and the paper cited \textit{in addition to} the software being cited.
%There are situations where it is appropriate to cite the software, the software paper, or both.

>>>>

Currently, and for the foreseeable future, software papers are being published and cited,
in addition to software itself being published and cited, as many community norms and practices are
oriented towards citation of papers.
As discussed in the Importance principle~(\ref{principle:importance}) and the discussion above, \textit{the software
itself should be cited on the same basis as any other research product; authors should cite the appropriate set of software products}.
If a software paper exists and it contains results (performance, validation, etc.) that are
important to the work, then the software paper should also be cited.
We believe that a request from the software authors to cite a paper should typically be respected, and the paper cited \textit{in addition to} the software.
